Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-08 talk/index.Rmd
resorted to live editor mermaid for experimental design diagram

@@

.panelset.sideways[
.panel[.panel-name[Introduction]
```{r, echo = FALSE, out.width='90%'}
knitr::include_graphics("images/introduction.png")
```
]

.panel[.panel-name[Prior Beliefs]

>>>>

---
class: left

# Experimental design

```{r, echo=FALSE, fig.align='center', out.width='80%', fig.retina=3}
knitr::include_graphics("images/mermaid.png")
```

@@

.panelset.sideways[
.panel[.panel-name[Introduction]
```{r, echo = FALSE, out.width='90%'}
knitr::include_graphics("images/introduction.png")
```
]
.panel[.panel-name[Prior Beliefs]
